---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# lazysql
Lazy SQL programming.
---------------------

Helper functions to create SQL expressions which can be
combined to SQL statements under program control.

Currently implemented are:

* `date_between` 	Create SQL string to select date between two given dates
* `in_condition` 	Create SQL string to select values included in a set of given values
* `natural_key` 	Create SQL string for joining on matching natural keys

## Sample usage
### date_between
```{r}
date1 <- as.Date("2016-02-22")
date2 <- as.Date("2016-02-11")
paste("select * from TEST_TABLE where", lazysql::date_between("STD_1", c(date1, date2)))
paste("select * from TEST_TABLE where", lazysql::date_between("STD_1", date1))
```
### in_condition
```{r}
lazysql::in_condition("COL_1", 1:3)
lazysql::in_condition("COL_1", 1:3, "not")
lazysql::in_condition("COL_1", LETTERS[2:3])
lazysql::in_condition("COL_1", LETTERS[2:3], "not")
```
### natural_key
```{r}
lazysql::natural_key(c("TAB1", "tab_2"),c("COL1", "col_2"))
```

